TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-07-24 paper/draft.tex
fix latex spacing complaints
more fig size tweaks

\begin{figure*}[h]
\begin{center}
	\includegraphics[width=.45\linewidth]{figures/cmd_teff_full.png}
	\includegraphics[width=.49\linewidth]{figures/cmd_teff_safe.png} \\
	\includegraphics[width=.45\linewidth]{figures/cmd_feh_full.png}
	\includegraphics[width=.49\linewidth]{figures/cmd_feh_safe.png} \\
	\includegraphics[width=.45\linewidth]{figures/cmd_spt_full.png}
	\includegraphics[width=.49\linewidth]{figures/cmd_spt_safe.png}
	\caption{Full sample of 14,827 M dwarfs colored by \cannon\ labels before selection (left) and final sample selection of 5,875 M dwarfs after applying selection criteria described in Section \ref{subsec:test_selection} (right), to reduce contamination from sources with that are not similar to the training sample (not single, main-sequence M stars, such as pre-main sequence, spectroscopic binaries, and K dwarfs). Overplotted with orange triangles are the M15 and W11 training samples, for their respective \cannon\ test labels. Temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly up from the main sequence branch as expected. Deviations from these gradients seen at the upper slice of the main sequence is likely remaining contamination from the binary sequence.}
	\label{fig:safe_selection}
\end{center}
\end{figure*}

\begin{figure*}[h]
	\includegraphics[width=\linewidth]{figures/aspcap_cannon_validation.png}
	\caption{\cannon\ (right column) and ASPCAP (left column) temperatures as compared to temperatures estimated color-temperature relations from three different literature sources for a subsample of 6,257 sources with $V,J,K$ colors. Shown are \cannon\ and ASPCAP temperatures (x-axis) compared to temperatures estimated from the \citealt{Mann:2015} $V-J$ and $\feh$ dependent relation (top), \citealt{Casagrande:2008} $V-K$ relation (middle), and the \citealt{Boyajian:2012} relation $V-K$ and $\feh$ (bottom).}
	\label{fig:teff_comparisons}
\end{figure*}

\begin{figure*}[h]
\begin{center}
	\includegraphics[width=5cm]{figures/met_comp1.png}
	\includegraphics[width=5cm]{figures/met_comp2.png}
	\includegraphics[width=5cm]{figures/met_comp3.png} 
	\includegraphics[width=5cm]{figures/met_comp4.png}
	\includegraphics[width=5cm]{figures/met_comp5.png}
	\includegraphics[width=5cm]{figures/met_comp6.png} 
	\includegraphics[width=5cm]{figures/met_comp7.png}
	\includegraphics[width=5cm]{figures/met_comp8.png}
	\includegraphics[width=5cm]{figures/met_comp9.png} 
	\caption{A comparison of ASPCAP and Cannon metallicities for 8,335 test sample sources separated into temperature bins of 100K. We see the scatter and metal-poor bias of ASPCAP metallicities clearly increases at decreasing temperatures.}
\end{center}
\end{figure*}

@@

\begin{figure*}[h]
	\begin{center}
	\includegraphics[width=16cm]{figures/demo_derivatives_teff1.png}
	\includegraphics[width=16cm]{figures/demo_derivatives_teff2.png}
	\end{center}
\end{figure*}

\begin{figure*}[h]
	\begin{center}
	\includegraphics[width=16cm]{figures/demo_derivatives_teff3.png}
	\end{center}
	\caption{\textit{Top two panels of each plot:} Mann-trained model for varying temperatures, and similar metallcities. \textit{Third panel of each plot:} Derivative of \thecannon\ model with respect to temperature, taken at the median training temperature, T$_{\rm eff}=3463$K; error estimate computed using a jackknife statistic at each pixel is marked in red, making it possible to distinguish which features vary significantly with change in spectral type, and which are likely due to noise.}
	\label{fig:demo_teff}
\end{figure*}

%---------------------------
\begin{figure*}[h]
	\begin{center}
	\includegraphics[width=16cm]{figures/demo_derivatives_feh1.png}
	\includegraphics[width=16cm]{figures/demo_derivatives_feh2.png}
	\end{center}
\end{figure*}

\begin{figure*}[h]
	\begin{center}
	\includegraphics[width=16cm]{figures/demo_derivatives_feh3.png}
	\end{center}
	\caption{\textit{Top two panels of each plot:} Mann-trained model for varying metallicities and similar temperatures. \textit{Third panel:} Derivative of \thecannon\ model with respect to metallicity, taken at the median training metallicity, $\feh=-0.03$\,dex; jackknife computed error at each pixel is shown in red.} \label{fig:demo_feh}
\end{figure*}

%---------------------------
\begin{figure*}[h]
	\begin{center}
	\includegraphics[width=12cm]{figures/Spectral_Sequence_1.png}
	\includegraphics[width=12cm]{figures/Spectral_Sequence_2.png}
	\includegraphics[width=12cm]{figures/Spectral_Sequence_3.png}
	\end{center}
	\caption{Spectral sequence of dwarfs in training set M0-M9; separate plots show three detector chips of \apogee\ spectrum (black), the best fit Cannon trained model (red) with highlighted spectral type sensitive regions identified in \citealt{Desphande:2013}.} \label{fig:sp_sequence}
\end{figure*}

%---------------------------
\begin{figure*}[h]
	\begin{center}
	\includegraphics[width=16cm]{figures/derivative_jackknife_spt.png}
	\end{center}
	\caption{Derivative plots for spectral type model taken at the median training spectral type, SPT$=3$; jackknife computed error at each pixel is shown in red.} 
	\label{fig:west_derivative}
\end{figure*}

% \begin{figure*}[h]
% 	\plotone{figures/spt_vs_teff_vs_feh.png}
% 	\caption{West-trained spectral types vs. Mann-trained metallcities and temperatures. For each integer spectral type bin the mean temperatures and metallicities are shown as red error boxes. \label{fig:west_vs_mann}}
% \end{figure*}

@@

% \begin{figure*}[h]
% 	\plotone{figures/mann_radii.png}
% 	\caption{Comparison of radii estimated from M15 relations: on the x-axis radii are derived from  K magnitudes and \cannon\ $\feh$, on the y-axis radii are derived from \cannon\ $\teff$ and $\feh$.}
% 	\label{fig:radii}
% \end{figure*}

>>>>

\begin{figure*}[]
\begin{center}
	\includegraphics[width=.45\linewidth]{figures/cmd_teff_full.png}
	\includegraphics[width=.48\linewidth]{figures/cmd_teff_safe.png} \\
	\includegraphics[width=.45\linewidth]{figures/cmd_feh_full.png}
	\includegraphics[width=.48\linewidth]{figures/cmd_feh_safe.png} \\
	\includegraphics[width=.45\linewidth]{figures/cmd_spt_full.png}
	\includegraphics[width=.48\linewidth]{figures/cmd_spt_safe.png}
	\caption{Full sample of 14,827 M dwarfs colored by \cannon\ labels before selection (left) and final sample selection of 5,875 M dwarfs after applying selection criteria described in Section \ref{subsec:test_selection} (right), to reduce contamination from sources with that are not similar to the training sample (not single, main-sequence M stars, such as pre-main sequence, spectroscopic binaries, and K dwarfs). Overplotted with orange triangles are the M15 and W11 training samples, for their respective \cannon\ test labels. Temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly up from the main sequence branch as expected. Deviations from these gradients seen at the upper slice of the main sequence is likely remaining contamination from the binary sequence.}
	\label{fig:safe_selection}
\end{center}
\end{figure*}

\begin{figure*}[]
\begin{center}
	\includegraphics[width=.9\linewidth]{figures/aspcap_cannon_validation.png}
	\caption{\cannon\ (right column) and ASPCAP (left column) temperatures as compared to temperatures estimated color-temperature relations from three different literature sources for a subsample of 6,257 sources with $V,J,K$ colors. Shown are \cannon\ and ASPCAP temperatures (x-axis) compared to temperatures estimated from the \citealt{Mann:2015} $V-J$ and $\feh$ dependent relation (top), \citealt{Casagrande:2008} $V-K$ relation (middle), and the \citealt{Boyajian:2012} relation $V-K$ and $\feh$ (bottom).}
	\label{fig:teff_comparisons}
\end{center}
\end{figure*}

\begin{figure*}[]
\begin{center}
	\includegraphics[width=.32\linewidth]{figures/met_comp1.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp2.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp3.png} 
	\includegraphics[width=.32\linewidth]{figures/met_comp4.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp5.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp6.png} 
	\includegraphics[width=.32\linewidth]{figures/met_comp7.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp8.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp9.png} 
	\caption{A comparison of ASPCAP and Cannon metallicities for 8,335 test sample sources separated into temperature bins of 100K. We see the scatter and metal-poor bias of ASPCAP metallicities clearly increases at decreasing temperatures.}
\end{center}
\end{figure*}

@@

\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{figures/demo_derivatives_teff1.png}
	\includegraphics[width=16cm]{figures/demo_derivatives_teff2.png}
	\end{center}
\end{figure*}

\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{figures/demo_derivatives_teff3.png}
	\end{center}
	\caption{\textit{Top two panels of each plot:} Mann-trained model for varying temperatures, and similar metallcities. \textit{Third panel of each plot:} Derivative of \thecannon\ model with respect to temperature, taken at the median training temperature, T$_{\rm eff}=3463$K; error estimate computed using a jackknife statistic at each pixel is marked in red, making it possible to distinguish which features vary significantly with change in spectral type, and which are likely due to noise.}
	\label{fig:demo_teff}
\end{figure*}

%---------------------------
\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{figures/demo_derivatives_feh1.png}
	\includegraphics[width=16cm]{figures/demo_derivatives_feh2.png}
	\end{center}
\end{figure*}

\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{figures/demo_derivatives_feh3.png}
	\end{center}
	\caption{\textit{Top two panels of each plot:} Mann-trained model for varying metallicities and similar temperatures. \textit{Third panel:} Derivative of \thecannon\ model with respect to metallicity, taken at the median training metallicity, $\feh=-0.03$\,dex; jackknife computed error at each pixel is shown in red.} \label{fig:demo_feh}
\end{figure*}

%---------------------------
\begin{figure*}[]
	\begin{center}
	\includegraphics[width=12cm]{figures/Spectral_Sequence_1.png}
	\includegraphics[width=12cm]{figures/Spectral_Sequence_2.png}
	\includegraphics[width=12cm]{figures/Spectral_Sequence_3.png}
	\end{center}
	\caption{Spectral sequence of dwarfs in training set M0-M9; separate plots show three detector chips of \apogee\ spectrum (black), the best fit Cannon trained model (red) with highlighted spectral type sensitive regions identified in \citealt{Desphande:2013}.} \label{fig:sp_sequence}
\end{figure*}

%---------------------------
\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{figures/derivative_jackknife_spt.png}
	\end{center}
	\caption{Derivative plots for spectral type model taken at the median training spectral type, SPT$=3$; jackknife computed error at each pixel is shown in red.} 
	\label{fig:west_derivative}
\end{figure*}

% \begin{figure*}[]
% 	\plotone{figures/spt_vs_teff_vs_feh.png}
% 	\caption{West-trained spectral types vs. Mann-trained metallcities and temperatures. For each integer spectral type bin the mean temperatures and metallicities are shown as red error boxes. \label{fig:west_vs_mann}}
% \end{figure*}

@@

% \begin{figure*}[]
% 	\plotone{figures/mann_radii.png}
% 	\caption{Comparison of radii estimated from M15 relations: on the x-axis radii are derived from  K magnitudes and \cannon\ $\feh$, on the y-axis radii are derived from \cannon\ $\teff$ and $\feh$.}
% 	\label{fig:radii}
% \end{figure*}
